MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-23 paper.Rmd
Matrix tables.

Several decisions influenced the design and APIs for the packages.
The decision involves data format. 
We selected the Physical Supply-Use Table (PSUT) data structure,
a matrix approach to describing energy flows from 
extraction to
processing stages and, ultimately, 
to final demand [@Rocco:2016; @Guevara:2017; @Heun:2018].
Given the decision to use PSUT matrices to store ECC data,
packages were created to enable manipulation of matrices
within the tidyverse, as shown in the following table.

| Package | Function |
|---------|----------|
| [RCLabels](https://github.com/MatthewHeun/RCLabels) | Manipulate row and column matrices |

@@

that different countries, 
and different years for a given country,
will have varying energy products and

>>>>

Several decisions influenced the design and APIs for the packages.
The decision involves data format. 
We selected the Physical Supply-Use Table (PSUT) framework,
a matrix approach to describing energy flows from 
extraction to
processing stages and, ultimately, 
to final demand [@Rocco:2016; @Guevara:2017; @Heun:2018].
The PSUT framework succinctly describes the flow of energy carriers
(products in PSUT terminology) 
among energy conversion machines 
(industries in PSUT terminology)
in a set of four matrices as described in the following table.

| Matrix | rows x columns     | Name            | Description                                              |
|:-------|:-------------------|:----------------|:---------------------------------------------------------|
| **R**  | industry x product | Resource matrix | Contains exogeneous energy inputs to an ECC              |
| **U**  | product x industry | Use matrix      | Describes how each energy conversion device uses energy  |
| **V**  | industry x product | Make matrix     | Describes how each energy conversion device makes energy |
| **Y**  | product x industry | Final demand matrix | Describes how each energy carrier is consumed        |

energy flows through various 
The matrix approach to data storage brings the challenge that 
different countries, 
and different years for a given country,
have varying energy products and varying energy processing machines.

Given the decision to use PSUT matrices to store ECC data,
packages were created to enable manipulation of matrices
within the tidyverse, as shown in the following table.

| Package | Function |
|---------|----------|
| [RCLabels](https://matthewheun.github.io/RCLabels/)      | Manipulate row and column matrices |
| [matsbyname](https://matthewheun.github.io/matsbyname/)  | Perform matrix mathematics that respects row and column names |

@@

that
